%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{0.9in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Joshua Kelly} & \href{mailto:jdjkelly@gmail.com}{jdjkelly@gmail.com} \\
  {CTO, Hacker, Artist} & +1 (647) 780 8114 \\
  \href{https://www.github.com/jdjkelly}{github.com/jdjkelly} & \href{https://angel.co/joshua-kelly}{angel.co/joshua-kelly} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Universe (part of NYSE:LYV)}{Toronto, ON}
      {Chief Technical Officer (CTO)}{Dec 2016 - Present}
      \resumeItemListStart
        \resumeItem{DIY Ticketing}
          {Universe is an international DIY platform for selling tickets. We power event ticketing for some of the most passionate fans in the world like \textbf{Blizzard Entertainment}'s annual Blizzcon. If you've been to a \textbf{TechCrunch Disrupt} recently, you've used our tech.}
        \resumeItem{Exit}
          {Acquired by \textbf{Live Nation Entertainment} (on behalf of their subsidiary, \textbf{Ticketmaster}) in 2015 for an undisclosed amount. Member of the original pre-acquisition team, hired as the second developer, and remaining the lead from 2013 until the acquisition. Provided technical specifications to Ticketmaster CTO during due diligence.}
     \resumeItemListEnd

    \resumeSubheading
      {Universe (part of NYSE:LYV)}{Toronto, ON}
      {Vice President, Engineering}{Dec 2016 - Present}
      \resumeItemListStart
        \resumeItem{Growth}
          {Led tech team through a period of 3x annualized growth in transactional volume - scaling the platform from \$x0M in annual gross ticket sales to \$x00M. Today, Universe has over 70 employees serving 12 international markets with offices in San Francisco, Toronto, and London.}
        \resumeItem{Tech Leadership}
          {Launched a developer platform (\href{https://developers.universe.com}{developers.universe.com}) and a \textbf{GraphQL API} - the first in the event industry.}
      \resumeItemListEnd

    \resumeSubheading
      {Universe}{Toronto, ON}
      {Senior Software Developer}{Apr 2012 - Nov 2016}
      \resumeItemListStart
        \resumeItem{VC-Backed Startup}
          {Pre-acquisition Universe, above, was initially a VC-backed startup (\textbf{Real Ventures}), raising \$2.5M.}
        \resumeItem{Architecture}
          {Designed and built version one of most of the core system applications, from the heart of our consumer facing checkout experience (embed.js) to complex data warehousing and ETL pipelines.}
        \resumeItem{Product Development}
          {Launched successful products during pivotal moments of company history. Successfully designed scaling solutions for the first high-volume Blizzcon, which exceeded Stripe's undisclosed transactional rate limit and required custom support on their end.}
      \resumeItemListEnd

    \resumeSubheading
      {Enginess (formerly Moveable Online)}{Toronto, ON}
      {Web Developer}{Jan 2011 - Mar 2012}
      \resumeItemListStart
        \resumeItem{Advantage WebStore}
          {Onboarded new clients on to a proprietary e-commerce platform for mid-sized retailers. Supported the rollout of the product's first bilingual store, designing and developing core product localization.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{DecentPost}
      {Winner of \textbf{Open Zeppelin Bounty} at \textbf{ETHDenver} 2018. A decentralized delivery protocol written in Solidity on top of Ethereum.}
    \resumeSubItem{\href{https://www.github.com/jdjkelly/transponder}{Transponder}}
      {A short-form decentralized messaging app built on Ethereum's contract event logs with Solidity and Truffle at \textbf{ETHWaterloo} 2017, to-date the largest Ethereum hackathon in the world.}
    \resumeSubItem{\href{https://www.github.com/jdjkelly/quant}{Quant}}
      {A quantified-self, self-hosted tracking platform with support for seveal major device manufacturers including FitBit and Withings (now Nokia).}
    \resumeSubItem{\href{https://www.github.com/jdjkelly/nockxir}{Nockxir}}
      {An Elixir-based interpreter for Urbit's Nock combinator VM.}
    \resumeSubItem{df8}
      {Winner of Music Hackday, Toronto. A distributed, collaborative music sequencer using mobile phones and WebSockets.}
    \resumeSubItem{(Redacted)}
      {A gallery installation in London. Using images crawled from a large social media app, I trained a generative adversarial network to produce a haunting series of artificial faces.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto (Trinity College)}{Toronto, ON}
      {Bachelor of Arts With Distinction}{Sep. 2006 -- Dec. 2010}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Elixir, JavaScript, Ruby, Python, Rust, SQL, R, Solidity}
    }
    \item{
      \textbf{Technologies}{: AWS, GCE, Kubernetes, Ethereum, Urbit, Postgres, MongoDB, Redis, vim, POSIX}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
